%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Certificates \& Training}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Altkom Akademia} % Organization
    {Advanced Python Training} % Title
    {Warsaw, Poland} % Location
    {Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Covered functional programming, advanced OOP, helper libraries, collections, regex, data processing, databases, threads and processes, asynchronous python, tests.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Scaled Agile, Inc.} % Organization
    {SAFe 5 Practitioner} % Title
    {Warsaw, Poland} % Location
    {Nov. 2020 (issued) - Nov. 2021 (expires)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Enabled me to work in the Scaled Agile Framework at T-Mobile.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {University of Toronto} % Organization
    {Self-Driving Cars Specialization} % Title
    {Coursera} % Location
    {2019 - 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Covered Path Tracking, State Estimation and Localization, Visual Perception, Motion Planning.}
        \item {Scored 95-100\% in each of the sections.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {EIT Digital} % Organization
    {Value Creation Through Innovation Specialization} % Title
    {Udacity} % Location
    {2020 - ongoing} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {The motivation to take this specialization was to understand the business value of the work I am doing now and will be doing in the future. The motivation came from working for www.o-ran.org.}
        \item {Covering The Impact Of Technology, Innovation \& Entrepreneurship, Marketing Strategies for Entrepreneurs, Capstone Value Creation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Udacity Nanodegree} % Organization
    {Cloud Developer} % Title
    {Udacity} % Location
    {May 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Deployed applications to AWS.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Udacity Nanodegree} % Organization
    {Full-Stack Developer} % Title
    {Udacity} % Location
    {May 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed several backend application in Flask.}
      \end{cvitems}
    }
    
%---------------------------------------------------------

\end{cventries}
