%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Engineer's Degree in Computer Science and Robotics} % Degree
    {Polish-Japanese Academy of Information Technology} % Institution
    {Warsaw, Poland} % Location
    {Oct. 2016 - Feb. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
       \item {Specialized in Robotics that included ML techniques, communication with the Roomba cleaner on the network and the remote steering of Arduino mini-cars.}
       \item {Graduated in the top 5\% of my class.}
       \item {Studies average: 4.54 out of 5.}
       \item {Language of instruction: English}
       \item {During the studies the biggest focus was put on Python, Machine Learning, SQL, Java, Algorithms, Arduino, teamwork and business applications.}
       \item {{\it Thesis topic:} The effect of lookahead distance of the Pure Pursuit controller’s cross-track error and comparison with the Stanley controller.}
       \item {{\it Thesis description:} developed PI, Pure Pursuit and Stanley controllers in the CARLA simulator to make a vehicle follow a path. Substituted a parameter to get better performance.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {ERASMUS+ exchange student in Computer Science} % Degree
    {Maynooth University} % Institution
    {Maynooth, Ireland} % Location
    {Oct. 2016 - Feb. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
       \item {An active member of business and IESN societies.}
       \item {Language of instruction: English}
       \item {Took an additional course on global issues such as education, gender, LGBTQIA+ and refugee inequalities around the world.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
