%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {T-Mobile} % Organization
    {Warsaw, Poland} % Location
    {Jul. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributing to an open-source solution for network automation called ONAP, part of The Linux Foundation.}
        \item {Building O-RAN Town to provide Open RAN technology.}
        \item {Became a recognized and a trusted committer in the integration project of ONAP responsible for developing new tests and functionalities.}
        \item {Developed new functionalities in Python SDK for ONAP according to internal business and external community requirements.}
        \item {Designed and created a Python wrapper for Helm charts to run network function simulators in tests.}
        \item {Led the decision making process for the operating model of the production environment.}
        \item {Created and managed development environments for several teams in GitLab CI/CD Pipelines.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\cventry
    {Machine Learning Teaching Assistant} % Job title
    {Polish-Japanese Academy of Information Technology} % Organization
    {Warsaw, Poland} % Location
    {Mar. 2020 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created teaching materials that covered classification/regression, kNN, Markov chain, perceptrons, CNNs/RNNs, autoencoders, fuzzy logic and Prolog.}
        \item {Taught 100 students above-mentioned topics by providing theoretical information followed by live coding.}
        \item {Consulted students who were struggling with the topics to ensure they understood the material after classes.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Lingaro} % Organization
    {Warsaw, Poland} % Location
    {Mar. 2019 - Oct. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created new functionalities for an IoT backend application responsible for managing remote IoT devices.}
        \item {Implemented push notifications that connected 1000 remote devices with their iOS apps through Azure Notification Hub in the production environment.}
        \item {Trained new teammates to help them understand the design and workflows of the backend app on UML diagrams.}
        \item {Took the 5th place in the internal competition from algorithms organized on codewars.com}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IT Support Intern} % Job title
    {Sun Valley Company} % Organization
    {Sun Valley, ID, USA} % Location
    {Jun. 2017 - Oct. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided conferences within the resort with Audiovisual/IT equipment.}
        \item {Supported the annual Allen \& Co. conference by providing equipment and technical support.}
        \item {Assisted the IT manager with setting up switches, routers and physical network connections.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
