%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Event organizer} % Affiliation/role
    {GDG Warsaw} % Organization/group
    {Warsaw, Poland} % Location
    {Oct. 2019 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Transforming local communities by organizing tech workshops.}
        \item {Have been delegated to Berlin (Germany) to promote Warsaw’s (Poland) community.}
        \item {Organized the 1st Polish nationwide DevFest 2020: searched for sponsors and developed the website.}
        \item {In 2021 a founder of the AI Jam series that promotes AI/ML through regular workshops and lectures.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Backend Developer} % Affiliation/role
    {Spark + AI Summit 2020 Hackathon for Social Good} % Organization/group
    {Poland \& USA} % Location
    {May 2020 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Trained a neural network model that made predictions about future COVID-19 cases per country.}
        \item {Developed endpoints that processed user requests and used a trained model to output predictions.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Backend Developer} % Affiliation/role
    {Hackathon by BEST Hacking League} % Organization/group
    {Warsaw, Poland} % Location
    {Apr. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developed backend for an application called StudyHub which meant to allow students to meet others in order to prepare for exams and/or regular classes together.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
